Can the symmetric \textit{Fermi} and eROSITA bubbles be produced by tilted jets: a proof-of-concept study

### 2022-03-28 paper.tex
update

\begin{subequations}
  \begin{align}
  &\frac{dE}{dtd\epsilon_{1}dV} =\nonumber\\
               &\frac{3}{4}\sigma_{T}c\mathbb{C}\epsilon_{1}\int^{\epsilon_{\text{max}}}_{\epsilon_{\text{min}}}
               \frac{n(\epsilon)}{\epsilon}d\epsilon\int^{\gamma_{\text{max}}}_{\gamma_{\text{min}}\left(\epsilon\right)}
               \gamma^{-(p+2)}f(q, \Gamma)d\gamma,\\
  \nonumber\\
  &f(q, \Gamma) =\nonumber\\
               &2q\ln q+(1+2q)(1-q)+0.5(1-q)\frac{\left(\Gamma q\right)^2}{1+\Gamma q},\\
  &q=\frac{\epsilon_{1}/\gamma\
               m_{\text{e}}c^{2}}{\Gamma\left(1-\epsilon_{1}/\gamma m_{\text{e}}c^{2}\right)},\\
  &\Gamma=\frac{4\epsilon \gamma}{m_{\text{e}}c^2},\\
  &\gamma_{\text{min}}(\epsilon)=\
   0.5\left(\frac{\epsilon_{1}}{m_{\text{e}}c^2}+\sqrt{\left(\frac{\epsilon_{1}}{m_{\text{e}}c^2}\right)^2+\
   \frac{\epsilon_{1}}{\epsilon}}\right) \label{gamma-min},
  \end{align}
\label{gammaray-emissivity}
\end{subequations}

where $\sigma_{T}$ is the Thomson cross section, $c$ is the speed of light,\
$m_{\text{e}}$ is the electron mass,\
$n(\epsilon)$ is the energy distribution of the photon number density in the ISRF given by \citet{Porter2017},\
$\gamma$ is the Lorentz factor of CRe, and\
$\mathbb{C}$ and $p$ are the normalization constant and spectral index of the CRe power-law spectrum.
$\gamma_{\text{min}}(\epsilon)$ is the minimum Lorentz factor of CRe\
that allows the incident photons to be scattered from energy $\epsilon$ to $\epsilon_{1}$, and\
$\gamma_{\text{max}}$ is the maximum CRe Lorentz factor in the spectrum. To obtain the simulated IC emissivities, we perform the double integration in Eq. \ref{gammaray-emissivity} on each cell\
over the range of the CRe Lorentz factor and\
the range of incident photon energy between\
$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (cosmic microwave background) and\
$\epsilon_{\text{max}}=13.59$ eV (optical starlight).\

@@

\section{Discussion}
Our modeled gamma-ray and microwave spectra assumed that
the underlying CRe spectrum is spatially uniform.
Therefore our results imply that, whatever the true re-acceleration and cooling mechanisms are,
the CRe spectrum at the present time has to be spatially uniform with
a spectral index of 2.4 in order to fit the observed spectra.

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{figures/fig__slice-compare.png}
  \caption
   {
    Simulation results based on the jets parameters in Fig. \ref{fig__jet_parameters}.
   }
  \label{fig__slice-compare}
\end{figure*}

>>>>

\begin{subequations}
  \begin{align}
  &\frac{dE}{dtd\epsilon_{1}dV} =\nonumber\\
               &\frac{3}{4}\sigma_{T}c\mathbb{C}\epsilon_{1}\int^{\epsilon_{\text{max}}}_{\epsilon_{\text{min}}}
               \frac{n(\epsilon)}{\epsilon}d\epsilon\int^{\gamma_{\text{e,max}}}_{\gamma_{\text{e,min}}\left(\epsilon\right)}
               \gamma_{\text{e}}^{-(p+2)}f(q, \Gamma)d\gamma_{\text{e}},\\
  \nonumber\\
  &f(q, \Gamma) =\nonumber\\
               &2q\ln q+(1+2q)(1-q)+0.5(1-q)\frac{\left(\Gamma q\right)^2}{1+\Gamma q},\\
  &q=\frac{\epsilon_{1}/\gamma_{\text{e}}\
               m_{\text{e}}c^{2}}{\Gamma\left(1-\epsilon_{1}/\gamma_{\text{e}} m_{\text{e}}c^{2}\right)},\\
  &\Gamma=\frac{4\epsilon \gamma_{\text{e}}}{m_{\text{e}}c^2},\\
  &\gamma_{\text{e,min}}(\epsilon)=\
   0.5\left(\frac{\epsilon_{1}}{m_{\text{e}}c^2}+\sqrt{\left(\frac{\epsilon_{1}}{m_{\text{e}}c^2}\right)^2+\
   \frac{\epsilon_{1}}{\epsilon}}\right) \label{gamma-min},
  \end{align}
\label{gammaray-emissivity}
\end{subequations}

where $\sigma_{T}$ is the Thomson cross section, $c$ is the speed of light,\
$m_{\text{e}}$ is the electron mass,\
$n(\epsilon)$ is the energy distribution of the photon number density in the ISRF given by \citet{Porter2017},\
$\gamma_{\text{e}}$ is the Lorentz factor of CRe, and\
$\mathbb{C}$ and $p$ are the normalization constant and spectral index of the CRe power-law spectrum.
$\gamma_{\text{e,min}}(\epsilon)$ is the minimum Lorentz factor of CRe\
that allows the incident photons to be scattered from energy $\epsilon$ to $\epsilon_{1}$, and\
$\gamma_{\text{e,max}}$ is the maximum CRe Lorentz factor in the spectrum. To obtain the simulated IC emissivities, we perform the double integration in Eq. \ref{gammaray-emissivity} on each cell\
over the range of the CRe Lorentz factor and\
the range of incident photon energy between\
$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (cosmic microwave background) and\
$\epsilon_{\text{max}}=13.59$ eV (optical starlight).\

@@

\section{Discussion}
Our modeled gamma-ray and microwave spectra assumed that
the underlying CRe spectrum is spatially uniform with hard spectral index 2.4;
however, the high energy CRe severely suffer from synchrotron and IC losses,
during their passage through the magnetic and radiation fields, respectively.

The typical synchrotron and IC cooling time scale of high energy ($\sim100$ GeV) CRe
in Milky Way is $\sim$ 1 Myr \citep{Yang2017}, ten times shorter than
12.39 Myr required for the simulated bubbles to reach the desired morphology.

Therefore, the CRe generating the gamma-ray emission would need to be re-accelerated
by in-situ acceleration mechanisms such as shocks or turbulence.
Since the forward shock is rather far away from the gamma-ray bubbles,
re-acceleration is more likely associated with turbulence \citep{Mertsch2011,Mertsch2019},
possibly in balance with the IC and synchrotron cooling. We will investigate the competition between stochastic acceleration and radiative cooling
in a future work.

Overall, our results imply that, whatever the true re-acceleration and cooling mechanisms are,
the CRe spectrum at the present time has to be spatially uniform with
a spectral index of 2.4 in order to fit the observed spectra.

%\begin{equation}
%   \frac{dE}{dt}
%     = -\frac{4}{3}\sigma_{T}c\beta_{\text{e}}^2\gamma_{\text{e}}^2
%     \left(U_{\text{photon}}+U_{B}\right),
%\end{equation}
%where $\beta_{\text{e}}=v_{\text{e}}/c$, $U_{\text{photon}}$ and $U_{B}$ are
%energy density of ISRF and magnetic field, respectively.

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{figures/fig__slice-compare.png}
  \caption
   {
    Simulation results based on the jets parameters in Table. \ref{tablb-jet-parameters}.
   }
  \label{fig__slice-compare}
\end{figure*}
